---
title: "R Notebook"
output: html_notebook
---

```{r}
rm(list=ls())
```


```{r}
library(readr)
library(xts)
library(fGarch)
library(moments)
library(ggplot2)
library(tseries)
library(rugarch)
library(extRemes)
library(secr)
```


```{r}
BK <- read_csv("BK.csv", 
    col_types = cols(Date = col_date(format = "%d/%m/%Y")))
```

```{r}
BK_price <- BK$`Adj Close`
date <- BK$Date
```

```{r}
dailyprice <- as.xts(BK_price,order.by=date)
```

```{r}
plot(dailyprice)
```


```{r}
return_series <- diff(log(dailyprice),lag=1)[-1,]
plot(return_series)
plot(abs(return_series), main = "Absolute Returns")
plot(return_series^2, main = "Squared Returns")
```

```{r}
mean <- mean(return_series,na.rm=TRUE)
```

```{r}
dailyvol <- return_series
dailyvol[] <- NA

dailyvol[,1] <- garchFit(~garch(1,1), data = return_series[,1])@sigma.t

```

```{r}
plot(dailyvol)
```

AC of Returns
```{r}
acf(return_series)
mtext('Autocorrelation of Returns', side = 3, line = -2, outer = TRUE, cex = 1.5)
pacf(return_series)
mtext('Partial Autocorrelation of Returns', side = 3, line = -2, outer = TRUE, cex = 1.5)
```

AC of Volatility
```{r}
acf(dailyvol, lag.max = 100)
mtext('Autocorrelation of volatility', side = 3, line = -2, outer = TRUE, cex = 1.5)
pacf(dailyvol)
mtext('Partial Autocorrelation of volatility', side = 3, line = -2, outer = TRUE, cex = 1.5)

```

Squared Returns
```{r}
sq_returns <- return_series^2
plot(sq_returns)
```
```{r}
acf(sq_returns, lag.max = 100)
mtext('Autocorrelation of Squared Returns', side = 3, line = -2, outer = TRUE, cex = 1.5)
pacf(sq_returns)
mtext('Partial Autocorrelation of Squared Returns', side = 3, line = -2, outer = TRUE, cex = 1.5)
```


```{r}
positive_returns <- return_series[return_series> 0]

negative_returns <- return_series[return_series< 0]

```

```{r}
zero_vector <- as.vector(matrix(0,nrow=length(return_series)))
regression <- cbind(Y=sq_returns,X1=lag(sq_returns,1),X2=pmax(zero_vector,lag(return_series,1), na.rm = TRUE),X3=pmin(zero_vector,lag(return_series,1),na.rm = TRUE))
regression[is.na(regression)] <-0 

lm_fit <- lm(Y ~ X1+X2+X3,regression)
summary(lm_fit)

anova(lm_fit)
```


```{r}
## Plots for theoretical argumentations 
dat <- return_series

d<- density(dat) # returns the density data
plot(d, xlab = "Returns", lty ="dotted",col="red", lwd =3, main = "Density comparison")
xfit<-seq(min(dat),max(dat),length=100) 
yfit<-dnorm(xfit,mean=mean(dat),sd=sd(dat)) 
lines(xfit, yfit, col="blue", lty = "dotted", lwd=2)
legend(-0.3, 30, legend=c("empirical density", "normal density"),
       col=c("red", "blue"), lty="dotted", cex=0.8)
```


```{r}

ggplot(regression, aes(x = X2)) + 
  geom_histogram(aes(y = ..density..), fill = 'blue', alpha = 0.5, binwidth = 0.001) + 
  geom_density(colour = 'red') + xlab(expression(bold('Time Series'))) + 
  ylab(expression(bold('Density')))

ggplot(regression, aes(x = X3)) + 
  geom_histogram(aes(y = ..density..), fill = 'blue', alpha = 0.5, binwidth = 0.001) + 
  geom_density(colour = 'red') + xlab(expression(bold('Time Series'))) + 
  xlab(expression(bold('Time Series'))) + 
  ylab(expression(bold('Density')))


```
Kurtosis and Skewness
```{r}
Kurtosis_Returns <- kurtosis(return_series, na.rm = TRUE)
Skewness_Returns <- skewness(return_series, na.rm = TRUE)
```


```{r}
scatter <- cbind(X=return_series,Y=lag(return_series))

ggplot(scatter, aes(y=scatter$X,x = scatter$Y)) + 
  geom_point() +
  geom_smooth(aes(),method=lm,se=FALSE,fill = "#3399FF", colour="#0000FF",size =1)  
```

## Estimate ARMA and GARCH models
 # Note: A GARCH process has zero mean by definition, so you would have to first
 # demean the return series, or jointly estimate an ARMA-GARCH model.
 
Demean returns

```{r}
returns_dm <- return_series - mean(return_series)

# Test
mean(returns_dm)
```
 

Model Nr. 1 ARMA(2,2)

```{r}
spec <- arfimaspec(mean.model=list(armaOrder=c(2,2)), distribution.model='std')
arma22 <- arfimafit(spec=spec,data=return_series)
show(arma22) # The 'shape' parameters corresponds to the DoF of the Student-t residuals.

likelihood(arma22)

st_resid_arma22 <- residuals(arma22,standardize=T)
acf(st_resid_arma22)
mtext('Autocorrelation of Standardized Residuals ARMA model', side = 3, line = -2, outer = TRUE, cex = 1.5)

Box.test(st_resid_arma22, lag = 1, type = "Ljung-Box", fitdf = 0)
Box.test(st_resid_arma22, lag = 5, type = "Ljung-Box", fitdf = 0)
Box.test(st_resid_arma22, lag = 10, type = "Ljung-Box", fitdf = 0)
Box.test(st_resid_arma22, lag = 20, type = "Ljung-Box", fitdf = 0)

```


Model Nr. 2 Garch

```{r}
spec <- ugarchspec(mean.model=list(armaOrder=c(0,0), include.mean=F),
                   variance.model=list(model='eGARCH', garchOrder=c(2,2)), distribution.model = "std")
garch11 <- ugarchfit(spec=spec,data=returns_dm)

csd_garch11 <- sigma(garch11) # Get fitted conditional standard deviations.
plot(csd_garch11)

st_resid_garch11 <- residuals(garch11,standardize=T)
plot(st_resid_garch11)

print(garch11)

acf(st_resid_garch11)
mtext('Autocorrelation of Standardized Residuals GARCH model', side = 3, line = -2, outer = TRUE, cex = 1.5)
Box.test(st_resid_garch11, lag = 1, type = "Ljung-Box", fitdf = 0)
Box.test(st_resid_garch11, lag = 5, type = "Ljung-Box", fitdf = 0)
Box.test(st_resid_garch11, lag = 10, type = "Ljung-Box", fitdf = 0)
Box.test(st_resid_garch11, lag = 20, type = "Ljung-Box", fitdf = 0)

qqnorm(st_resid_garch11, main = "Normal vs Empirical distribution standardized returns GARCH(1,1)"); qqline(st_resid_garch11, col ="red", lty =2, lwd = 2)

```


Model Nr. 3 GJR - Garch

```{r}
spec <- ugarchspec(mean.model=list(armaOrder=c(0,0), include.mean=F),
                   variance.model=list(model='gjrGARCH', garchOrder=c(1,1)), distribution.model = "std")
gjrgarch11 <- ugarchfit(spec=spec,data=returns_dm)

csd_gjrgarch11 <- sigma(garch11) # Get fitted conditional standard deviations.
plot(csd_gjrgarch11)

plot(c(csd_gjrgarch11,csd_garch11))

st_resid_gjrgarch11 <- residuals(gjrgarch11,standardize=T)
plot(st_resid_gjrgarch11)

qqnorm(st_resid_gjrgarch11 , main = "Normal vs Empirical distribution standardized returns GJR-GARCH"); qqline(st_resid_garch11, col ="red", lty =2, lwd = 2)

# acf and pacf of standardized residuals show no ac

print(gjrgarch11)

acf(st_resid_gjrgarch11)
mtext('Autocorrelation of Standardized Residuals GJR-GARCH model', side = 3, line = -2, outer = TRUE, cex = 1.5)

Box.test(st_resid_gjrgarch11, lag = 1, type = "Ljung-Box", fitdf = 0)
Box.test(st_resid_gjrgarch11, lag = 5, type = "Ljung-Box", fitdf = 0)
Box.test(st_resid_gjrgarch11, lag = 10, type = "Ljung-Box", fitdf = 0)
Box.test(st_resid_gjrgarch11, lag = 20, type = "Ljung-Box", fitdf = 0)


garch11_likelihood <- likelihood(garch11)
gjrgarch11_likelihood <- likelihood(gjrgarch11)
likelihood <- lr.test(garch11_likelihood, gjrgarch11_likelihood, alpha = 0.05, df = 1)
print(likelihood)
```

===========
Exercise 2:
===========

```{r}
VaR_result <- data.frame(matrix(nrow = 3, ncol = 4), stringsAsFactors = FALSE)
rownames(VaR_result) <- c("Standard", "Forecast GARCH", "Simulation GARCH")
colnames(VaR_result) <- c("1 % VaR","5 % VaR","1 % ES","5 % ES")
VaR_result
```


```{r}
#end_date <- "/2008-09-12"
end_date <- "/2008-10-6"
sub_sample_returns <- return_series[end_date]
plot(sub_sample_returns)
```

Set up

```{r}
std_sub_sample <- sd(sub_sample_returns)
mean_sub_sample <-  mean(sub_sample_returns)

position <- 1000000

quantile_easy_way <- c('5% VaR'=qnorm(0.05),'1% VaR'=qnorm(0.01))
```

```{r}
var_easy_way <- (1-exp((mean_sub_sample + quantile_easy_way*std_sub_sample))) * position
var_easy_way

VaR_result[1,2] <- var_easy_way[1]
VaR_result[1,1] <- var_easy_way[2]

```


```{r}
quantile <- c('5% ES'=quantile(sub_sample_returns, 0.05),'1% ES'=quantile(sub_sample_returns, 0.01))

es_easy_way_5 <- (1-exp(mean(sub_sample_returns[sub_sample_returns < quantile[1]]))) * position
es_easy_way_5
es_easy_way_1 <- (1-exp(mean(sub_sample_returns[sub_sample_returns < quantile[2]]))) * position
es_easy_way_1

VaR_result[1,3] <- es_easy_way_1
VaR_result[1,4] <- es_easy_way_5

```


With GARCH
```{r}
#plot(return_series["2008-09-10/2008-09-16"])
```

```{r}
spec <- ugarchspec(mean.model=list(armaOrder=c(0,0), include.mean=F),
                   variance.model=list(model='sGARCH', garchOrder=c(1,1)),
                   distribution.model='std')

sub_sample_garch <- ugarchfit(spec=spec,data=sub_sample_returns)
dof <- coef(sub_sample_garch)[4] # Estimated DoF of Student-t residuals
sub_sample_csd <- ugarchforecast(sub_sample_garch,n.ahead = 1)
sub_sample_csd <- as.numeric(sigma(sub_sample_csd))


#Simulation Returns Distribution

simulation <- ugarchsim(sub_sample_garch, n.sim = 1, n.start = 0, m.sim = 10000, startMethod = "sample", rseed = 10)
print(simulation)


returns_simulation <- sub_sample_returns
returns_simulation[2] <- t(simulation@simulation$seriesSim)
plot(returns_simulation)
mtext('Simulation of Returns Distribution', side = 3, line = -2, outer = TRUE, cex = 1.5)

# Forecast tomorrows conditional standard deviation.
```

```{r}
a <- c('5% VaR'=0.95,'1% VaR'=0.99)
wealth <- 1000000
var_garch_r <- qt(1-a,dof)*sub_sample_csd + mean_sub_sample # VaR in log-returns / use 'qnorm' for Gaussian residuals.

var_garch_w <- wealth*(1-exp(var_garch_r))
var_garch_w

var_simulation_5 <- quantile(returns_simulation, 0.05, na.rm = TRUE)
var_simulation_1 <- quantile(returns_simulation, 0.01, na.rm = TRUE)


VaR_result[2,1] <- var_garch_w[2]
VaR_result[2,2] <- var_garch_w[1]
VaR_result[3,2] <- abs(var_simulation_5*wealth)
VaR_result[3,1] <- abs(var_simulation_1*wealth)
```

# ES from a GARCH model
# Note: If no explicit formula exists, you can always simulate.
# If X is uniformly distributed over [0,1] and F is an inverse cumulative
# distribution function for some distribution D, then F(X) is D-distributed.
X <- runif(1000,min=0,max=1) # Draw 1000 values uniformly in [0,1]
Y <- qt(X,dof) # Convert to Student-t. Alternatively use 'rt'.
L <- wealth*(1-exp(csd*Y + r.m)) # Simulate loss distribution.
es_garch_w <- mean(L[L>var_garch_w])

```{r}
X <- runif(1000,min=0,max=1) # Draw 1000 values uniformly in [0,1]
Y <- qt(X,dof) # Convert to Student-t. Alternatively use 'rt'.
L <- wealth*(1-exp(sub_sample_csd*Y + mean_sub_sample)) # Simulate loss distribution.
VaR_result[2,4] <- mean(L[L>var_garch_w[1]])
VaR_result[2,3] <- mean(L[L>var_garch_w[2]])

Distribution_5 <- mean(returns_simulation[returns_simulation<= var_simulation_5])
Distribution_1 <- mean(returns_simulation[returns_simulation<= var_simulation_1])
VaR_result[3,4] <- abs(Distribution_5*wealth)
VaR_result[3,3] <- abs(Distribution_1*wealth)
```

```{r}
#return_series["2008-09-15"]

return_series["2008-10-7"]

(1-exp(return_series["2008-09-15"]))*position
(1-exp(return_series["2008-10-07"]))*position

VaR_result
```


